COG-ED Manuscript

### 2021-12-09 06_Paper/COG-ED/Manuscript.Rmd
prepare results display of h2b
prepare tables and figures
start writing resulst and methods
added new hypothesis

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.

@@

To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
**MLM explanation goes here** To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 92 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 100 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
The multi-level model will be run with each of the 92 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100 ms, removal of post-error trials).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

@@

```{r Hypothesis_2b, echo=FALSE, message=FALSE, warning=FALSE}

@@

  ## maximal model ----

  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
                 data = h2b_sub,
                 REML = T) # parameters estimated by maximizing restricted log-likelihood

@@

  library(interactions)

  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                                       # print conditional intercepts
                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals, 
                                                                        # create plot, adjust false discovery rate
  library(huxtable)
  as_huxtable(m1_h2b.ss)

  plot(m1_h2b.ss)

  interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                x.label = "n back load level", y.label = "subjective value", legend.main = "NFC", interval = T) + theme_apa()

  # FIXME: Do not print all charts

  # prepare results for reporting ----------------------------------------------

  names(summary(m1_h2b))
  m1_h2b.fixef <- summary(m1_h2b)$coefficients
  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)

  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef), 
                                          m1_h2b.fixef[,c(1, 2, 5)]))
  h2b_result.table$ranef.sd <- NA
  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
  colnames(h2b_result.table)[1] <- "Parameter"
  colnames(h2b_result.table)[2] <- "Beta"
  colnames(h2b_result.table)[3] <- "SE"
  colnames(h2b_result.table)[4] <- "p-Value"
  colnames(h2b_result.table)[5] <- "Random Effects (SD)"

@@

  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)],"*")
  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)],"*")
  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)],"*")

  # FIXME: display of p = 0.000,  no display of NA

  apa_table(h2b_result.table,
            caption = "Subjective values decline with increasing n-back level, even after controlling for declining task 
            performance (d’ and reaction time), correct and postcorrect trials.",
            note = "")

@@

  # TODO: 
    # -> check whether we want to include an additional hypothesis
    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores" 
    # What do you think?

@@

(`r apa_table(h2b_result.table)`)

intraclass correlation "icc_h2b"

huxtable?

@@

>>>>

Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
Regarding the associations of subjective and objective task load we hypothesize that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with n-back level.
Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
(2c) or (3a) or (3b) "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores"

@@

To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
+ NFC
**MLM explanation goes here**

fit using $lmerTest$ package
# center level 1 predictors
 two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
 level 1 predictor (SV) is of substantive interest
 CWC
# level 2 predictor
 CGM
null model > ICC
random slopes model
  controlled for performance (d', RT), correct and post-correct trials
parameter estimation REML
include model?
simple slopes analysis

To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 92 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 100 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
The multi-level model will be run with each of the 92 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100 ms, removal of post-error trials).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

@@

```{r Hypothesis_2b, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}

@@

  ## maximal model ---- 
  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
                 data = h2b_sub,
                 REML = T) # parameters estimated by maximizing restricted log-likelihood

@@

  library(interactions)
  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                                       # print conditional intercepts
                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals, 
                                                                        # create plot, adjust false discovery rate

  # prepare MLM results for reporting ------------------------------------------

  # get random and fixed effects
  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
  m1_h2b.fixef <- summary(m1_h2b)$coefficients

  # prepare table
  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef), 
                                          m1_h2b.fixef[,c(1, 2, 5)]))
  h2b_result.table$ranef.sd <- NA
  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]

  colnames(h2b_result.table)[1] <- "Parameter"
  colnames(h2b_result.table)[2] <- "Beta"
  colnames(h2b_result.table)[3] <- "SE"
  colnames(h2b_result.table)[4] <- "p-Value"
  colnames(h2b_result.table)[5] <- "Random Effects (SD)"

@@

  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)],"*")
  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)] <- 
    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)],"*")
  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)] <- 
    paste0("<.001***")

  h2b_result.table$`Random Effects (SD)`[3:8] <- paste0("")

  library(kableExtra)
  #replication_table <-
    kbl(h2b_result.table,
    caption = "Effects of n-back load level on subjective value controlled 
    for task performance (d’ and reaction time), correct and postcorrect trials.",
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote
  #FIXME delete leading zero for p-values

  # prepare SSA results for reporting ------------------------------------------

  m1_h2b.ss$slopes

  library(huxtable)
  h2b_ssa.table <- as_huxtable(m1_h2b.ss)
  h2b_ssa.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
  h2b_ssa.table <- h2b_ssa.table[-2,]

  h2b_ssa.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")

  # create interaction plot
  h2b_ssa.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                                x.label = "n back load level", y.label = "subjective value",
                                legend.main = "NFC", interval = T) + theme_apa()

@@

    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores"

@@

The multilevel model `r replication_table`

statistically significant effect of n-back load level `r apa_print(m1_h2b)$full_result$level_cwc`
controlled for performance and correct and post-correct answers

`r apa_print(m1_h2b)$full_result$nfc_cgm`
`r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).

simple slopes analysis `r h2b_ssa.table`, `r h2b_ssa.plot`
statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC

@@

# Discussion

# (summary and interpretation of h2b_results)
